Supplementary Appendix

### 2023-11-22 manuscript/supplement.qmd
minor wording corrections

Besides the usage of `Git` and remote repositories as a version control systems, there are further relevant aspects that determine the reproducibility of analytic code when using open-source software such a R. To complement the introduction and discussion on `Git` in the main manuscript, we here want to elaborate on a few further considerations of computational reproducibility when using R.

>>>>

Besides the usage of `Git` and remote repositories as a version control systems, there are further relevant aspects that determine the reproducibility of analytic code when using open-source software such as R. To complement the introduction and discussion on `Git` in the main manuscript, we here want to elaborate on a few further considerations addressing the computational reproducibility when using R.
